Fusing Filters with Integer Linear Programming

### 2014-05-15 2014betterfusionforfilters/section/06-Related.tex
Typo

Ultimately, the job of an array fusion system is to make the program go as fast as possible on the available hardware. Although the cost metrics of ``optimal'' fusion systems try to model the performance behavior of this hardware, it is not practical to encode the intricacies of all available hardware in a single compiler implementation. Iterative compilation approaches such as~\cite{ashby2006iterative} instead enumerate many possible clusterings, use a the cost metric to rank them, and perform benchmark runs to identify which clustering actually performs the best. An ILP formulation like ours naturally supports this model, as the integer constraints define the available clusterings, and the objective function can be used to rank them.

>>>>

Ultimately, the job of an array fusion system is to make the program go as fast as possible on the available hardware. Although the cost metrics of ``optimal'' fusion systems try to model the performance behavior of this hardware, it is not practical to encode the intricacies of all available hardware in a single compiler implementation. Iterative compilation approaches such as~\cite{ashby2006iterative} instead enumerate many possible clusterings, use a cost metric to rank them, and perform benchmark runs to identify which clustering actually performs the best. An ILP formulation like ours naturally supports this model, as the integer constraints define the available clusterings, and the objective function can be used to rank them.
